\section{Dependencies}
Dependencies include softwares or framework that need to be installed for proper working of this software.

\emph{{\large There is no software dependencies to Install this software.}}

This software could be installed on any given list of operating system.

\begin{enumerate}
	\item Mac OS X
	\item Windows
	 \begin{enumerate} 
	 	\item XP or newer on x86 32/64 bit
	 \end{enumerate}
	\item Linux
	\begin{enumerate} 
		\item Debian 
		\item Ubuntu 
		\item Kubuntu
		\item Arch Linux
		\item openSUSE
		\item Fedora
	 \end{enumerate}
	\item BSD
	\begin{enumerate}
		\item NetBSD  $\geq 6.1$
		\item FreeBSD $\geq 10 $
		\item OpenBSD
	\end{enumerate}
\end{enumerate}	 
 

But If you want to build OpenSCAD this software from soucre code on \emph{any OS}, you need some libraries and tools. The version
numbers in brackets specify the versions which have been used for
development. Other versions may or may not work as well.

If you're using a newer version of Ubuntu, you can install these 
libraries from aptitude. If you're using Mac, or an older Linux/BSD, there 
are build scripts that download and compile the libraries from source. 
Follow the instructions for the platform you're compiling on below.

\begin{enumerate} 
	\item A C++ compiler supporting C++11
	
	\item Qt$  4.4 \rightarrow 5.x $ (http://qt.io/ )
	
	\item QScintilla2 $ (2.7 \rightarrow $)(http://www.riverbankcomputing.co.uk/software/qscintilla/)
	
	\item CGAL ($ 3.6 \rightarrow $) (http://www.cgal.org/)
	
	\item GMP (5.x) (http://www.gmplib.org/)
	
	\item MPFR (3.x)(http://www.mpfr.org/)
	
	\item cmake ($ 2.8 \rightarrow $, required by CGAL and the test framework))(http://www.cmake.org/)
	
	\item boost ($ 1.35 \rightarrow $) (http://www.boost.org/)
	
	\item OpenCSG ($ 1.3.2 \rightarrow $)(http://www.opencsg.org/)
	
	\item GLEW ($ 1.5.4 \rightarrow $)(http://glew.sourceforge.net/)
	
	\item Eigen (3.x)(http://eigen.tuxfamily.org/)
	
	\item glib2 (2.x)(https://developer.gnome.org/glib/)
	
	\item fontconfig ($ 2.10 \rightarrow  $)(http://fontconfig.org/)
	
	\item freetype2 ($ 2.4 \rightarrow  $)(http://freetype.org/)
	
	\item harfbuzz ($ 0.9.19 \rightarrow  $)(http://harfbuzz.org/)
	
	\item Bison ($ 2.4 \rightarrow $ )(http://www.gnu.org/software/bison/)
	
	\item Flex ($ 2.5.35 \rightarrow  $)(http://flex.sourceforge.net/)
	
	\item pkg-config ($ 0.26 \rightarrow $ )(http://www.freedesktop.org/wiki/Software/pkg-config/)
	
\end{enumerate}


