\section{Conclusion}

This project was something which required in-depth view in designing the programming language and analysis of your problems.
The main problem in this project was encountered during this project was related to writing a parser that is able to parse the context sensitive grammar while also keeping the big chunk of context-free grammar part of language separate.
Even with this major problem we were able to finish this project before the set time and provide the user with the work which they can use, test and provide feedback.

A great deal of things are learned while working on this project. The learning was not limited to project only but
the whole experience of working as a trainee under Dr. H.S. Rai at TCC, developer at OpenSCAD and also as a mentor for Google Code In was immensely educational. Working with the Open Source Community and a variety of people of different age group, one is always challenged by the fundamental difference between classroom coaching and real World experience. But such a challenge is exactly the purpose of six months training.

The whole experience of working on this project and contributing to a few others has been very
rewarding as it has given great opportunities to learn new things and get a firmer grasp on already
known technologies. Here is a reiteration of some of the technologies I have encountered, browsed and learned:
\begin{enumerate}
    \item Operating System: Linux
    \item Language: C++, flex, bison, JSON, \LaTeX
    \item FrameWork: Qt, Travis CI
    \item Softwares: Git, cTest, GRASS GIS, Doxygen
    \item Building Tools: qmake, CMake, make
    \item Communication tools: IRC
\end{enumerate}
So during this project, I learned all the above things. Above all, I got to know how software is
developed and how much work and attention to details is required in building even the most basic
of components of any project. Apart from above I also learned things like:
\begin{enumerate}
    \item Planning
    \item Designing
    \item Developing code
    \item Working in a team
    \item Testing
    \item Licensing Constraints
    \item How Open source community work?
    \item Writing Readable code
    \item Coding Standards
\end{enumerate}
And these are all very precious lessons in themselves.