\section{Future Scope}
OpenSCAD being an open source project and supported by a large open Source community have a lot of scope for future improvements and additions as other individuals can also contribute in it and add additional functionality. One of the examples is my project only customizer for OpenSCAD.

Being an Open Source project there is a constant flow of suggestion and demands by people for additional functionality and improvement in existing features.
Customizer being no exception constant flow of feature of suggestions and feature requests even before the start of development. Here is a small list of the Features that would be added in near future.

\begin{enumerate}

\item \textbf{Adding support for InBuid syntax:} It was decided much at beginning of the project that this feature will be ported using a special syntax then relying on the comment based syntax. The discussion has been going on related to deciding the syntax for the customizer.  

\item \textbf{Option to Add images:} It has been proposed that there should be a feature to add images through customizer.

\item \textbf{Option to Include files with Customizer:} This feature will help people change the include file with the help of Customizer which could provide a feature which would be related to Run Time Polymorphism.

\item \textbf{Conditional display of Parameter in customizer:} Sometimes people want to show a different set of parameters based on the chooses made by the user before that parameter or sometimes we just want to hide the parameters because of the selection made by the user in the pervious parameter.

\item \textbf{Improving GUI part:} There have been some suggestions related to improving the GUI of the Customizer
https://github.com/openscad/openscad/issues/1845 .
\item \textbf{Providing syntax to manipulate modules parameter:} This feature will help user pick a customized version of the module using the customizer. They will be able to Customize the parameters of modules using and the Customizer than drag that into the file to call it with customized parameter.
\end{enumerate}

Apart from these features, their are Some suggestion related to how existing feature would be improved to refer to that you can visit following:

\begin{enumerate}
    \item https://github.com/openscad/openscad/issues/1844
    \item https://github.com/openscad/openscad/issues/1840
    \item https://github.com/openscad/openscad/issues/1781
    \item https://github.com/openscad/openscad/issues/722
\end{enumerate}