\section{Conclusions}
This project was something which required in-depth view in analysis of your problems. The main problem in this project was encountered during the research process. The sheer size of the software to be studied was daunting and required intense efforts to even begin to understand. And it was not possible to contribute anything without understanding the working of the whole process. This was because the project was not about adding a new feature but improving an existing central feature by almost completely changing its design. Time is always an eternal challenge. Completing such a task required one's undivided attention and it was certainly challenging to do it with other academic responsibilities.
A great deal of things were learned while working on this project. The experience of working with an open source community is always wonderfull. We got to interact and exchange views with some of the technological leaders of this field during this project.
The whole experience of working on this project and contributing to a few others has been very rewarding as it has given great opportunities to learn new things and get a firmer grasp on already known technologies. Here is a reiteration of some of the technologies I have encountered, browsed and learned:
\begin{itemize}
	\item Operating system: Linux
	\item Language: C++
	\item Framework: Qt
	\item Software: Git, cTest, Doxygen
	\item Building Tools: qmake, CMake, make
	\item Communication tools: IRC
\end{itemize}
So during this project, we learnt all the above things. Above all, we got to know how software is developed and how much work and attention to details is required in building even the most basic of components of any project of this size. Apart from above we also learnt things like:
\begin{itemize}
	\item Planning
	\item Designing
	\item Reading code
	\item Developing code
	\item Working on a team
	\item Testing standards
	\item Licensing constraints
	\item Working of open source community
	\item Writing readable code
	\item Coding standards
\end{itemize}
