\section{Feasibility Study}
Feasibility study aims to uncover the strengths and weaknesses of 
a project. In its simplest term, the two criteria to judge feasibility 
are cost required and value to be attained. As such, a well-designed 
feasibility analysis should provide a historical background of the 
project, description of the project or service, details of the 
operations and management and legal requirements. Generally, feasibility 
analysis precedes technical development and project implementation. 
These are some feasibility factors by which we can determine that 
project is feasible or not:
\begin{itemize}
\item {\bf{Technical feasibility}}: Technological feasibility is carried 
out to determine whether the project has the capability, in terms of 
software, hardware, personnel to handle and fulfill the user requirements. This whole project is based on Open 
Source Environment and is part of a open souce software which would be deployed on any OS.

\item {\bf{Economic feasibility}}: In Economic feasibitly we 
determine whether the benefit is gain according to the cost invested 
to develop the project or not. If benefits outweigh costs, only then 
the decision is made to design and implement the system. It is 
important to identify cost and benefit factors, which can be categorized 
as follows:
\begin{enumerate}
\item Development costs.
\item Operating costs.
\end{enumerate}
OpenSCAD's customizer is also Economically feasible with as It could be developed and maintain with zero cost as It is supported by Open source community.
Plus This project is started with no intention of having any economic gain but still their are option of donations. 

\end{itemize}


